\newpage
\fancyhead[C]{Thomas Turner}
\section{Custom Hardware} \label{section:Custom Hardware}
\subsection{Introduction}\label{sub_section:tgt_custom_hardware_intro}
\gls{COTS} options should always be considered before custom parts, as they do not incur the significant design, testing, and compliance costs. However, due to the specific harsh operating environment and the design goals of the project, specific components will be custom-made. Both flight controllers and \gls{GNSS} modules are high-priced items that would benefit from specific designs for this application and are explored. All designs should support modularity, redundancy, performance, and be lower in price than \gls{COTS} options. They should also line up with our sustainability and inclusion objectives by ensuring all components are \gls{ROHS} compliant and, where applicable, should support those with disabilities.

\input{Thomas/Custom_Hardware/PCBS}
\input{Thomas/Custom_Hardware/1_General_Design}
\input{Thomas/Custom_Hardware/2_Custom_Components}

\subsection{Conclusion}
Both designed modules are cheaper than \gls{COTS} options and meet the design requirements. They support field and in-depth debugging using an \gls{LED} array, easy-to-access headers, and the \gls{CAN} bus. The LED array also considers those with colour blindness, and all components are \gls{ROHS} compliant in line with our sustainability and inclusion objectives. Lastly, the designs support redundancy in sensors, modules, and communication to ensure that the risk of failure is mitigated. However, the success of the design is dependent on further testing and compliance with regulations. Therefore, the next steps are to manufacture prototypes for internal testing and real-world trials before applying for CE and then UA DoC compliance. This will enable these devices to be deployed in Ukraine and the European Union. To deploy in further jurisdictions, further compliance tests will be needed to satisfy local laws. 