\subsection{Risk Analysis}\label{sub_section:tgt_risk}
\subsubsection{Ground Operator Owned Risks}\label{sub_sub_section:tgt_ground_operator_risk} \input{Thomas/Safety_and_Risk/risk_matrix}
\input{Thomas/Safety_and_Risk/risk_register_ground}
\paragraph{Boot Testing}
Before the start of any mission, the flight controller gives standard control signals directly after take-off. If the sensor recordings match the expected results for the control signals, the mission goes ahead. If there is an actuator fault, the sensors will all record similar results different from the expected results, and if there is a sensor fault, the sensors will all record the expected results except for the faulty sensor. Furthermore, all communication lines are tested to check they are operable, even if they are redundant. This isolates any module faults so that they can be replaced and sent for repair.
\paragraph{Role of Design}
The design of the device should support ground operators at all times. Therefore, clear and easy documentation will be provided, and all interfaces are as simple and easy to use as possible. However, in order to continue to support progress, feedback must be gathered to improve the design in a testing phase and throughout operation.

\subsubsection{Designer Owned Risks}\label{sub_sub_section:tgt_design_risk}
\input{Thomas/Safety_and_Risk/risk_register_design} 
\paragraph{Designed Redundancy}
Reducing the risk of failure through redundancy is a key mitigation to the primary high severity risks as shown in Table \ref{tab:risk_register_designer}. This, in combination with regular field testing, means that the risk of failure is a low as reasonably possible, as all modules and redundant modules are tested regularly, so it would require a common mode failure, a catastrophic failure, or a dual failure.
\paragraph{Analysis and updates}
During testing and deployment, if there are failures, they need to be analysed and addressed. This requires a designed level of support for analysis, improvement, and replacement. For analysis, there is a removable memory device for all telemetry and error messages, in addition to easy debugging methods. For improvements, all designed hardware has the specifications to add functionality by ensuring it exceeds the current requirements. Finally, for replacement, all modules can be replaced easily with different specification versions. This design level flexibility is vital for the longevity of the design. Furthermore, to ensure that the device is as affordable as possible, the risk matrices are re-evaluated regularly with the deployment data to isolate areas that are overly mitigated. For example, if it is found that the \gls{GNSS} module has a negligible chance of failure, the redundant \gls{GNSS} modules can be removed from the device to reduce unit cost, allowing for the further reduction in demining costs.
\paragraph{Intellectual Property}
 To maintain the standing of the company and ensure quality in the company's products, there will be a trademark in place for the company name and logo. However, for ethical reasons, as explored in Section \ref{sustainability}, all designs and underlying technology will be open-source to allow for the most innovation in this critical field.