\newpage
\fancyhead[C]{Thomas Turner}
\section{Return to Safety} \label{Return to Safety}

\subsection{Introduction and Philosophy}
\textbf{NEEDS A REWRITE}
Traditionally \gls{RTH} is executed in commercial drone products in case of detected faults. This specific use case provides cause to expand this functionality. In cases of partial thrust failure, provided it is not above the critical value needed to maintain stability, the \gls{UAV} will have to use less aggressive control in order to cause no further degeneration and compensate for lower actuator saturation levels. This makes the \gls{UAV} less robust to disturbances and therefore introduces a significant probability of crashing. Similarly, if the battery state of charge is depleting faster than predicted and hence causing a state of charge failure you can model this as a probability of failure at any given point given the unpredictability of degenerating cells \cite{REF}. Lastly, if adverse weather conditions are detected causing instability, similarly to if there is partial thrust failure, the device can no longer be assumed to be robust to the environmental disturbances and has a significant probability of crashing. Given the difficulty of retrieval, this means that traditional \gls{RTH} is not the optimal strategy in these specific cases and instead a \gls{RTS} strategy is more appropriate.
\paragraph{When to use \gls{RTH}}
\gls{RTH} is always preferable to to \gls{RTS} as by tracing back the original path returns the device to the base on an obstacle free path. Therefore, \gls{RTH} should be used when the device is robust to the environmental conditions, and when the device has accurate location sensing for avoidance of large obstacles and obstructions. This means in cases of redundant sensor or communication faults, non safety critical sensor faults, or if commanded by the base station, \gls{RTH} should be executed.
\paragraph{Objectives}
The objective of the \gls{RTS} system is to provide a robust path planning route to safe landing zones when \gls{RTH} is not possible. It should also be easy to setup and operate by untrained ground operators.

\input{Thomas/Return_To_Safety/1_Cost_Maps}
\input{Thomas/Return_To_Safety/2_Fault_Detection_And_Control}
\input{Thomas/Return_To_Safety/3_Path_Planning}